The pollination trade-off

### 2018-03-20 publication/manuscript.Rmd
Small changes to results

The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A). 
In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B). 
For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree.

```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "Trade off predictions j."}
loadd(trade_off_predictions, model_linear_fits, tidied_fixed)

@@

p2 <- trade_off_predictions %>%
  mutate_at(c("conspecific", "heterospecific"), exp) %>%
  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
  filter(!(value > 2.2 & term == "k")) %>%
  humanize() %>%
  ggplot(aes(x = value, y = gain, colour = term)) +
  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
  geom_point(shape = 21, alpha = 0.5, size = 1) +
  geom_smooth(aes(fill = term), 
              se = F, size = 0.5, method = "glm", 
              method.args = list(family = "binomial"), alpha = 0.1)+
  pub_theme() +
  scale_color_manual(values = colour_scale_values) +  
  scale_fill_manual(values = colour_scale_values) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "top") +
  labs(colour = "", fill = "", 
       y = "proportion conspecific pollen gain", 
       x = "scaled variable value")

>>>>

The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A). 
In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B). 
For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).

```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen. (A) Overall and species-level relationship. Grey lines indicate the relationship in each of the samples, the median is indicated with a black solid line. Dotted lines show the relationship for each species. Invasive species are shown in red. (B) The proportion of conspecific pollen relative to the total amount of pollen gained trough animal pollination and its relationship to our set of explanatory variables."}
loadd(trade_off_predictions, model_linear_fits, tidied_fixed)

@@

p2 <- trade_off_predictions %>%
  mutate_at(c("conspecific", "heterospecific"), exp) %>%
  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
  filter(!(value > 2.2 & term == "k")) %>%
  humanize() %>%
  ggplot(aes(x = value, y = gain, colour = term)) +
  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
  geom_point(shape = 21, alpha = 0.5, size = 1) +
  geom_smooth(aes(fill = term), 
              se = F, size = 0.5, method = "glm", 
              method.args = list(family = "binomial"), alpha = 0.1)+
  pub_theme() +
  scale_color_manual(values = colour_scale_values) +  
  scale_fill_manual(values = colour_scale_values) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "top") +
  labs(colour = "", fill = "", linetype = "", 
       y = "proportion conspecific pollen gain", 
       x = "scaled variable value")
